\ifx\AllTogetherMode\undefined%
\IfFileExists{../prefix.tex}%
{\input{../prefix}}%
{\input{prefix}}%
\fi

\HomeworkStart%
{9} % Homework number
{12} % Week of semester submitted
{1.01} % Version

\SaveIndent%
\HWInstructionsStd{}%

\HWInstructions{%

   % Do not use hashing or dictionary data-structures in the solutions
   % of the questions here.
   Any dynamic programming solution should be done using an iterative
   algorithm.

}

\noindent%


\begin{questions}[start=25]
    \RestoreIndent%

    \item

    \HWProblem{100}{Rainbow walk}{ We are given a directed graph with
       $n$ vertices and $m$ edges ($m\ge n$), where each edge $e$ has
       a color $c(e)$ from $\{1,\ldots,k\}$.

       \begin{questions}
           \item \points{20} Describe an algorithm, as fast as
           possible, to decide whether there exists a closed walk that
           uses all $k$ colors.  (In a walk, vertices and edges may be
           repeated.  In a closed walk, we start and end at the same
           vertex.)

           \item \points{80} Now, assume that there are only 3 colors,
           i.e., $k=3$.  Describe an algorithm, as fast as possible,
           to decide whether there exists a walk that uses all 3
           colors.  (The start and end vertex may be different.)
       \end{questions}

    }{}{}{}

    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \item \HWProblem{100}{Stay safe}{ We are given an
       \emph{undirected} graph with $n$ vertices and $m$ edges
       ($m\ge n$), where each edge $e$ has a positive real weight
       $w(e)$, and each vertex is marked as either ``safe'' or
       ``dangerous''.

       \begin{questions}
           \item \points{35} Given safe vertices $s$ and $t$, describe
           an $O(m)$-time algorithm to find a path from $s$ to $t$
           that passes through the smallest number of dangerous
           vertices.

           \item \points{65} Given safe vertices $s$ and $t$ and a
           value $W$, describe an algorithm, as fast as possible, to
           find a path from $s$ to $t$ that passes through the
           smallest number of dangerous vertices, subject to the
           constraint that the total weight of the path is at most
           $W$.
       \end{questions}

    }{}{}{}


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \item \HWProblem{100}%
    {Stay stable}%
    {%
       We are given a directed graph with $n$ vertices and $m$ edges
       ($m\ge n$), where each edge $e$ has a weight $w(e)$ (you can
       assume that no two edges have the same weight).  For a cycle
       $C$ with edge sequence $e_1e_2\cdots e_\ell e_1$, define the
       \emph{fluctuation} of $C$ to be
       \[
           f(C) = |w(e_1)-w(e_2)| + |w(e_2)-w(e_3)| + \cdots +
           |w(e_\ell)-w(e_1)|.
       \]

       \begin{questions}
           \item \points{10} Show that the cycle with the minimum
           fluctuation cannot have repeated vertices or edges, i.e.,
           it must be a simple cycle.
           \item \points{90} Describe a polynomial-time algorithm, as
           fast as possible, to find the cycle with the minimum
           fluctuation.
       \end{questions}


    }{}{}{}

\end{questions}


\HomeworkEnd{}

